Qualitative Probabilistic Programming

### 2015-06-05 paper/paper.tex
example cleanup: randFunction(Cluster, Point)

var Cluster = Categorical(2);
var Point = Vector(2, Double);
var getPoint = randFunction(Categorical(2), pointType);
return function() {
  repeat(n, function(i) {
    var cluster = randomValue(Cluster);
    observe(getPoint, cluster);
  });
};
  \end{verbatim}

>>>>

var Cluster = Categorical(2);
var Point = Vector(2, Double);
var getPoint = randFunction(Cluster, Point);
return function() {
  repeat(n, function(i) {
    var cluster = randomValue(Cluster);
    observe(getPoint, cluster);
  });
};
  \end{verbatim}
